Re-fit

### 2022-08-03 scripts/r/04_refit/refit_jvc.Rmd
update code to fix issues describes in #123

#
# JVC refits
#
MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
  mutate(measure_z = (measure - mean(measure)) / sd(measure),
    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
  filter(condition == "AF")

gymnothorax_spinulosus_1_intdiff_con <- brm(
  measure_z ~ effect_con + 
    (1|target_colour) + 
    (1|speaker), 
  data = MSA_gymnothorax_spinulosus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
  )

@@

@@

Processed data not available.

@@

trigonias_lachneri_1_spi_con <- brm(
  spi_z ~ effect_con, 
  data = MSA_trigonias_lachneri_spi_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  file = here("data", "analyses", "models", "trigonias_lachneri_1_spi_con")
  )

>>>>

#
# JVC refits
#
MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
  mutate(measure_z = (measure - mean(measure)) / sd(measure),
    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean), 
    typ_mean_z = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
  filter(condition == "AF")

gymnothorax_spinulosus_1_intdiff_con <- brm(
  measure_z ~ effect_con * typ_mean_z + 
    (1|target_colour) + 
    (1|speaker), 
  data = MSA_gymnothorax_spinulosus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  control = list(max_treedepth = 14), 
  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
  )

@@

# JVC: load data

msa_lycodes_bradfieldi <- read_csv(here("data", "analyses", "jvc", 
  "lycodes_bradfieldi", "processed-data", "all_trial_data_nas_removed.csv")) %>% 
  mutate(typicality = as.factor(typicality), 
    effect_cat = C(typicality, treatment), 
    effect_cat = fct_relevel(effect_cat, "atypical")
)

@@

Processed data does not include DVs.

@@

trigonias_lachneri_1_spi_con <- brm(
  spi_z ~ effect_con + 
    (1 + typ_mean|target_colour) + 
    (1 + typ_mean|speaker),
  data = MSA_trigonias_lachneri_spi_data, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", 
  control = list(adapt_delta = 0.99), 
  file = here("data", "analyses", "models", "trigonias_lachneri_1_spi_con")
  )
